---
title: "With_Cubic_Interpolation"
author: "Peian Lu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(graphics)
library(tibble)
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(ggcorrplot)
library(mlr)
library(tidyverse)

```

### offline data main
```{r}
#data = read.csv( "C:/Users/85212/Desktop/Pro-Data/main.csv" ,header=TRUE) 
data = read.csv("C:/Users/85212/Desktop/Pro-Data/online.csv", header=TRUE)
#names(data) = c( 'Sample.Key',names(data)[-1] )
#data = data[-1,]
data= data[,-2]
colnames(data)[1]='EFT..Hours'
names(data)
ac = read.csv( "C:/Users/85212/Desktop/Pro-Data/acids.csv" ,header=TRUE) 
names(ac) = c( 'Date',names(ac)[-1] )
```


## Merging by Cubic Spline Interpolation
```{r}
x = ac$EFT
y = ac$acetic
x_out = data$EFT..Hours
interpolated_acetic = spline(x = x ,y = y , xout = x_out )
data1 = cbind(data, interpolated_acetic$y) %>% filter( EFT..Hours < 360)
```

## Plot 
```{r}

plot( Interpolated_acetic$x,  Interpolated_acetic$y , type ='p', pch='.' ,col = 1 , xlab = 'EFT' , ylab = 'acetic' , main='Plot of interpolated values')
points(ac$EFT , ac$acetic,col=2)
legend("topright", inset=.05, c('Interpolation',"Real"),lty=c(1, 1), pch=c(1, 1), col=c(1, 2))

```

```{r}
dim(data1)
dim( as.data.frame( data1[complete.cases(data1) ,] )   )
```


## Pre-process
```{r}
colnames(data1)[68] = 'interpolated_acetic' 
data1 =  data1[complete.cases(data1) ,]
data1$interpolated_acetic[ which(data1$interpolated_acetic < 0 )] = 0
remove_col = c()
for (j in 1:dim(data1)[2] )
{
  if (  mean(data1[,j]) < 0.01 | min(data1[,j])  == mean(data1[,j])  )
  remove_col = c(remove_col , j)
  else
  {
    wrong_row = which(data1[,j] < 0 )
    data1[wrong_row , j] = 0
  }
  
}
data1 = data1[,-remove_col]
summary(data1)
```

## Imputation
```{r}
imputeMethod = imputeLearner("regr.rpart")
data1Imp = impute(as.data.frame(data1), classes = list(numeric = imputeMethod) )

```

## Plot 
```{r}
data1_gather = gather(data1[,c(1:10,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()

data1_gather = gather(data1[,c(11:20,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()
data1_gather = gather(data1[,c(21:30,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()

data1_gather = gather(data1[,c(31:40,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()

data1_gather = gather(data1[,c(41:50,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()

data1_gather = gather(data1[,c(51:60,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()

data1_gather = gather(data1[,c(61:67,68)], key = "Variable",
value = "Value", -c(  interpolated_acetic  ) )
ggplot(data1_gather, aes(Value, interpolated_acetic)) +
facet_wrap(~ Variable, scale = "free_x") +
geom_point() +
geom_smooth(method = "lm", col = "blue") +
theme_bw()
```

# Setting Task
```{r}
AceticTask = makeRegrTask(data = data1Imp$data, target = "interpolated_acetic")
```


## Features importance by random forest
```{r}
filterVals = generateFilterValuesData(AceticTask, method = "randomForest_importance")
plotFilterValues(filterVals , n.show = 7) + 
theme_bw()
```


## Generating and plotting filter values by correlation
```{r}
filterVals = generateFilterValuesData(AceticTask)
plotFilterValues(filterVals , n.show = 6) + theme_bw()
```
## GLM
```{r}
gamTask = makeRegrTask(data = data1Imp$data, target = "interpolated_acetic")

imputeMethod = imputeLearner("regr.rpart")
gamImputeWrapper = makeImputeWrapper("regr.gamboost")

gamFeatSelControl = makeFeatSelControlSequential(method = "sfbs")
kFold = makeResampleDesc("CV", iters = 2)

gamFeatSelWrapper = makeFeatSelWrapper(learner = gamImputeWrapper,
resampling = kFold,
control = gamFeatSelControl)
```
## CV
```{r}
Holdout = makeResampleDesc("Holdout")
gamCV = resample(gamFeatSelWrapper, gamTask, resampling = Holdout)
gamCV
```
## Training
```{r}
library(parallel)
library(parallelMap)
parallelStartSocket(cpus = detectCores())
gamModel = train(gamFeatSelWrapper, gamTask)
parallelStop()
gamModelData = getLearnerModel(gamModel, more.unwrap = TRUE)
```

# Lasso
## Training
```{r}
lasso = makeLearner("regr.glmnet", alpha = 1, id = "lasso")
lassoParamSpace = makeParamSet(
makeNumericParam("s", lower = 0, upper = 15))

parallelStartSocket(cpus = detectCores())

cvForTuning = makeResampleDesc("RepCV", folds = 10, reps = 3)
randSearch = makeTuneControlRandom(maxit = 200)

tunedLassoPars = tuneParams(lasso, task = AceticTask,
resampling = cvForTuning,
par.set = lassoParamSpace,
control = randSearch)
parallelStop()
tunedLassoPars
```

```{r}
lassoTuningData = generateHyperParsEffectData(tunedLassoPars)
plotHyperParsEffect(lassoTuningData, x = "s", y = "mse.test.mean",
plot.type = "line") +
theme_bw()
```

```{r}
tunedLasso = setHyperPars(lasso, par.vals = tunedLassoPars$x)
tunedLassoModel = train(tunedLasso, AceticTask)
lassoModelData = getLearnerModel(tunedLassoModel)
lassoCoefs = coef(lassoModelData, s = tunedLassoPars$x$s)
lassoCoefs
```
## Plot
```{r}
coefTib = tibble(Coef = colnames(data1)[-1] )

coefTib$LASSO <- as.vector(lassoCoefs)[-1]
coefUntidy = gather(coefTib, key = Model, value = Beta, -Coef)
ggplot(coefUntidy, aes(reorder(Coef, Beta), Beta, fill = Model)) +
geom_bar(stat = "identity", col = "black") +
facet_wrap(~ Model) +
theme_bw() +
theme(legend.position = "none")
```
# Elastic net model
```{r}
elastic = makeLearner("regr.glmnet", id = "elastic")
elasticParamSpace = makeParamSet(
makeNumericParam("s", lower = 0, upper = 10),
makeNumericParam("alpha", lower = 0, upper = 1))
randSearchElastic = makeTuneControlRandom(maxit = 400)
parallelStartSocket(cpus = detectCores())
tunedElasticPars = tuneParams(elastic, task = AceticTask,
resampling = cvForTuning,
par.set = elasticParamSpace,
control = randSearchElastic)
parallelStop()
tunedElasticPars
```
## Plot
```{r}
elasticTuningData = generateHyperParsEffectData(tunedElasticPars)
plotHyperParsEffect(elasticTuningData, x = "s", y = "alpha",
z = "mse.test.mean", interpolate = "regr.kknn",
plot.type = "heatmap") +
scale_fill_gradientn(colours = terrain.colors(5)) +
geom_point(x = tunedElasticPars$x$s, y = tunedElasticPars$x$alpha,
col = "white") +
theme_bw()
```

## Training with best parameters
```{r}
tunedElastic = setHyperPars(elastic, par.vals = tunedElasticPars$x)
tunedElasticModel = train(tunedElastic, AceticTask)
```

## Plotting the model parameters
```{r}
elasticModelData = getLearnerModel(tunedElasticModel)
elasticCoefs = coef(elasticModelData, s = tunedElasticPars$x$s)
coefTib$Elastic = as.vector(elasticCoefs)[-1]
coefUntidy = gather(coefTib, key = Model, value = Beta, -Coef)
ggplot(coefUntidy, aes(reorder(Coef, Beta), Beta, fill = Model)) +
geom_bar(stat = "identity", position = "dodge", col = "black") +
facet_wrap(~ Model) +
theme_bw()
```

# Benchmarking ridge, LASSO, elastic net, and OLS

## Plot
```{r}
# ridgeWrapper = makeTuneWrapper(ridge, resampling = cvForTuning,
# par.set = ridgeParamSpace,
# control = randSearch)
lassoWrapper = makeTuneWrapper(lasso, resampling = cvForTuning,
par.set = lassoParamSpace,
control = randSearch)

elasticWrapper = makeTuneWrapper(elastic, resampling = cvForTuning,
par.set = elasticParamSpace,
control = randSearchElastic)

learners = list(elasticWrapper, lassoWrapper, "regr.lm") # elasticWrapper,ridgeWrapper

kFold3 = makeResampleDesc("CV", iters = 2)
parallelStartSocket(cpus = detectCores())
bench = benchmark(learners, AceticTask, kFold3)
parallelStop()
bench
```
## Refit regression by variables selected by Lasso
```{r}
Coef = as.numeric( lassoCoefs)
index = which(Coef!=0)[-c(1)]  ## remove EFT.h EFT.acid and intercept
variables = rownames(lassoCoefs)[index]
print(variables)
names(data1)[index-1]
reg = lm(interpolated_acetic~., data1Imp$data[, c(index-1,68)] )
summary(reg)
CoefReg = coef(reg)
plot(reg)

pred = predict(reg , data1Imp$data[, c(index-1,68)])
pred[ which(pred<0)    ] = 0

plot(pred, (data1[,68] - pred ) , xlab = 'fitted_value' , ylab = 'residuals', main = 'residual plot with correction')
plot(data1$EFT..Hours , pred , xlab='ETF',ylab='acetic value' , col = 2 , pch = 2)
points(data1$EFT..Hours , data1$interpolated_acetic , type='p' , col = 1 , pch = 1)
legend("topright", cex = 0.8, c('fitted values',"real values"),lty=c(1, 1), pch=c(2, 1), col=c(2, 1))

```
## Lm stepwise
```{r}
lmstep = step( lm(interpolated_acetic~., data = data1)   ) 
plot(lmstep)

pred_step = predict(lmstep ,  data1 )
pred_step[ which(pred_step<0)    ] = 0

plot(pred_step, (data1[,68] - pred ) , xlab = 'fitted_value' , ylab = 'residuals', main = 'residual plot with correction')
plot(data1$EFT..Hours , pred_step , xlab='ETF',ylab='acetic value' , col = 2 , pch = 2 , main = 'with step_wise model')
points(data1$EFT..Hours , data1$interpolated_acetic , type='p' , col = 1 , pch = 1)
legend("topright", cex = 0.8, c('fitted values',"real values"),lty=c(1, 1), pch=c(2, 1), col=c(2, 1))
```

## Box-cox 
```{r}
library(MASS)
epsilon = 1e-4
boxData1 =   data1Imp$data[ , c(index - 1,68) ]
zeroRow = which( data1Imp$data$interpolated_acetic ==0)  
boxData1$interpolated_acetic[zeroRow] = boxData1$interpolated_acetic[zeroRow] + epsilon

b = boxcox( interpolated_acetic ~. , data= boxData1  , plotit = F)
trans = b$x[ which.max(b$y) ]

boxCoxReg = lm(  interpolated_acetic^trans ~. ,   data= data1Imp$data[ , c(index - 1,68) ] )
summary(boxCoxReg)
plot(boxCoxReg)

```

