---
title: "Caret"
author: "Peian"
date: '2022-07-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(AppliedPredictiveModeling)
transparentTheme(trans = .4)
library(caret)
library(gbm)
library(mboost)
library(KRLS) # Polynomial Kernel Regularized Least Squares
library(monomvn) # Bayesian Ridge Regression (Model Averaged)
library(doParallel)
```

```{r}
unregister_dopar <- function() {
  env <- foreach:::.foreachGlobals
  rm(list=ls(name=env), pos=env)
}
```

```{r}
featurePlot(x = iris[, 1:4], 
            y = iris$Species, 
            plot = "pairs",
            ## Add a key at the top
            auto.key = list(columns = 3))
```
```{r}
library(mlbench)
data(BostonHousing)
regVar <- c("age", "lstat", "tax")
str(BostonHousing[, regVar])

featurePlot(x = BostonHousing[, regVar], 
            y = BostonHousing$medv, 
            plot = "scatter",
            type = c("p", "smooth"),
            span = .5,
            layout = c(3, 1))
```
## 3.2 Zero- and Near Zero-Variance Predictors

```{r}
data(mdrr)
data.frame(table(mdrrDescr$nR11))
nzv <- nearZeroVar(mdrrDescr, saveMetrics= TRUE)
nzv[nzv$nzv,][1:10,]

nzv <- nearZeroVar(mdrrDescr)
filteredDescr <- mdrrDescr[, -nzv]
filteredDescr
```
## 3.3 Identifying Correlated Predictors

```{r}
descrCor <-  cor(filteredDescr)
highCorr <- sum(abs(descrCor[upper.tri(descrCor)]) > .999)
highCorr
```

```{r}
highlyCorDescr <- findCorrelation(descrCor, cutoff = .75)
filteredDescr <- filteredDescr[,-highlyCorDescr]
descrCor2 <- cor(filteredDescr)
summary(descrCor2[upper.tri(descrCor2)])
```

## 3.4 Linear Dependencies
The function `findLinearCombos`
```{r}
ltfrDesign <- matrix(0, nrow=6, ncol=6)
ltfrDesign[,1] <- c(1, 1, 1, 1, 1, 1)
ltfrDesign[,2] <- c(1, 1, 1, 0, 0, 0)
ltfrDesign[,3] <- c(0, 0, 0, 1, 1, 1)
ltfrDesign[,4] <- c(1, 0, 0, 1, 0, 0)
ltfrDesign[,5] <- c(0, 1, 0, 0, 1, 0)
ltfrDesign[,6] <- c(0, 0, 1, 0, 0, 1)
```

```{r}
comboInfo <- findLinearCombos(ltfrDesign)
comboInfo
```

```{r}
ltfrDesign[, -comboInfo$remove]
```

## 3.6 Centering and Scaling
```{r}
set.seed(96)
inTrain <- sample(seq(along = mdrrClass), length(mdrrClass)/2)

training <- filteredDescr[inTrain,]
test <- filteredDescr[-inTrain,]
trainMDRR <- mdrrClass[inTrain]
testMDRR <- mdrrClass[-inTrain]

preProcValues <- preProcess(training, method = c("center", "scale"))

trainTransformed <- predict(preProcValues, training)
testTransformed <- predict(preProcValues, test)
```
## 3.8 Transforming Predictors
### Box-Cox
```{r}
preProcValues2 <- preProcess(training, method = "BoxCox")
trainBC <- predict(preProcValues2, training)
testBC <- predict(preProcValues2, test)
preProcValues2
```

## 3.9 Putting It All Together
```{r}
library(AppliedPredictiveModeling)
data(schedulingData)
str(schedulingData)
```

```{r}
pp_hpc <- preProcess(schedulingData[, -8], 
                     method = c("center", "scale", "YeoJohnson"))
pp_hpc
```
```{r}
transformed <- predict(pp_hpc, newdata = schedulingData[, -8])
head(transformed)
```

```{r}
pp_no_nzv <- preProcess(schedulingData[, -8], 
                        method = c("center", "scale", "YeoJohnson", "nzv"))
pp_no_nzv
predict(pp_no_nzv, newdata = schedulingData[1:6, -8])
```
# 4 Data Splitting
## 4.1 Simple Splitting Based on the Outcome
```{r}
library(caret)
set.seed(3456)
trainIndex <- createDataPartition(iris$Species, p = .8, 
                                  list = FALSE, 
                                  times = 1)
irisTrain <- iris[ trainIndex,]
irisTest  <- iris[-trainIndex,]
```

## 4.2 Splitting Based on the Predictors
Also, the function `maxDissim` can be used to create sub–samples using a maximum dissimilarity approach (Willett, 1999).

```{r}
library(mlbench)
data(BostonHousing)

testing <- scale(BostonHousing[, c("age", "nox")])
set.seed(5)
## A random sample of 5 data points
startSet <- sample(1:dim(testing)[1], 5)
samplePool <- testing[-startSet,]
start <- testing[startSet,]
newSamp <- maxDissim(start, samplePool, n = 20)
head(newSamp)
```
## 4.4 Simple Splitting with Important Groups
Confused.
```{r}
set.seed(3527)
subjects <- sample(1:20, size = 80, replace = TRUE)
table(subjects)
folds <- groupKFold(subjects, k = 15) 
folds
```

# 5 Model Training and Tuning
## 5.1 Model Training and Parameter Tuning

```{r}
library(mlbench)
data(Sonar)
str(Sonar[, 1:10])
library(caret)
set.seed(998)
inTraining <- createDataPartition(Sonar$Class, p = .75, list = FALSE)
training <- Sonar[ inTraining,]
testing  <- Sonar[-inTraining,]
```

## 5.3 Basic Parameter Tuning
To use a random search, use the option search = "random" in the call to trainControl. In this situation, the tuneLength parameter defines the total number of parameter combinations that will be evaluated.
```{r}
fitControl <- trainControl( method = "repeatedcv", number = 10, repeats = 10 , classProbs = TRUE, search = "random" )
```

```{r}
set.seed(825)
gbmFit1 <- train(Class ~ ., data = training, 
                 method = "gbm", 
                 trControl = fitControl,
                 ## This last option is actually one
                 ## for gbm() that passes through
                 verbose = FALSE)
gbmFit1
```

## 5.4 Notes on Reproducibility
To set the model fitting seeds, `trainControl` has an additional argument called seeds that can be used.

### 5.5.2 Alternate Tuning Grids
```{r}
gbmGrid <-  expand.grid(interaction.depth = c(1, 5, 9), 
                        n.trees = (1:30)*50, 
                        shrinkage = 0.1,
                        n.minobsinnode = 20)
                        
nrow(gbmGrid)

set.seed(825)
gbmFit2 <- train(Class ~ ., data = training, 
                 method = "gbm", 
                 trControl = fitControl, 
                 verbose = FALSE, 
                 ## Now specify the exact models 
                 ## to evaluate:
                 tuneGrid = gbmGrid,
                 metric = "ROC")
gbmFit2
```

```{r}
fitControl <- trainControl(method = "repeatedcv",
                           number = 10,
                           repeats = 2,
                           ## Estimate class probabilities
                           classProbs = TRUE,
                           ## Evaluate performance using 
                           ## the following function
                           summaryFunction =  twoClassSummary
                           )

set.seed(825)
gbmFit3 <- train(Class ~ ., data = training, 
                 method = "gbm", 
                 trControl = fitControl, 
                 verbose = FALSE, 
                 tuneGrid = gbmGrid,
                 ## Specify which metric to optimize
                 metric = "ROC",tuneLength = 8)
gbmFit3
```


## 5.6 Choosing the Final Model
```{r}
whichTwoPct <- tolerance(gbmFit3$results, metric = "ROC", 
                         tol = 2, maximize = TRUE)  
cat("best model within 2 pct of best:\n")
gbmFit3$results[whichTwoPct,1:6]
```
## 5.7 Extracting Predictions and Class Probabilities
```{r}
predict(gbmFit3, newdata = head(testing))
predict(gbmFit3, newdata = head(testing), type = "prob")
```

### 5.8.2 Between-Models
Benchmarking
```{r}
set.seed(825)
svmFit <- train(Class ~ ., data = training, 
                 method = "svmRadial", 
                 trControl = fitControl, 
                 preProc = c("center", "scale"),
                 tuneLength = 8,
                 metric = "ROC")
set.seed(825)
rdaFit <- train(Class ~ ., data = training, 
                 method = "rda", 
                 trControl = fitControl, 
                 tuneLength = 4,
                 metric = "ROC")
```

```{r}
resamps <- resamples(list(GBM = gbmFit3,
                          SVM = svmFit,
                          RDA = rdaFit))
resamps
```

```{r}
bwplot(resamps, layout = c(3, 1))
```
## 5.9 Fitting Models Without Parameter Tuning
If we have already a tunning parameter
```{r}
fitControl <- trainControl(method = "none", classProbs = TRUE)

set.seed(825)
gbmFit4 <- train(Class ~ ., data = training, 
                 method = "gbm", 
                 trControl = fitControl, 
                 verbose = FALSE, 
                 ## Only a single model can be passed to the
                 ## function when no resampling is used:
                 tuneGrid = data.frame(interaction.depth = 4,
                                       n.trees = 100,
                                       shrinkage = .1,
                                       n.minobsinnode = 20),
                 metric = "ROC")
gbmFit4
predict(gbmFit4, newdata = head(testing))
```

# 9 Parallel Processing
```{r}
cl <- makePSOCKcluster( detectCores())
registerDoParallel(cl)

## All subsequent models are then run in parallel
model <- train(Class ~ ., data = training, method = "rf")

## When you are done:
stopCluster(cl)
```

# 15 Variable Importance
```{r}
gbmImp <- varImp(gbmFit3, scale = FALSE)
gbmImp
```
## 20.3 Recursive Feature Elimination via caret
```{r}
library(caret)
library(mlbench)
library(Hmisc)
library(randomForest)

n <- 100
p <- 40
sigma <- 1
set.seed(1)
sim <- mlbench.friedman1(n, sd = sigma)
colnames(sim$x) <- c(paste("real", 1:5, sep = ""),
                     paste("bogus", 1:5, sep = ""))
bogus <- matrix(rnorm(n * p), nrow = n)
colnames(bogus) <- paste("bogus", 5+(1:ncol(bogus)), sep = "")
x <- cbind(sim$x, bogus)
y <- sim$y
normalization <- preProcess(x)
x <- predict(normalization, x)
x <- as.data.frame(x)
subsets <- c(1:5, 10, 15, 20, 25)
set.seed(10)

ctrl <- rfeControl(functions = lmFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x, y,
                 sizes = subsets,
                 rfeControl = ctrl)

lmProfile
```



